%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{Finlay_Maguire_CV}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Finlay}{Maguire}{ \urlstyle{same}\href{http://finlaymagui.re}{finlaymagui.re} | \href{http://github.com/fmaguire}{github/fmaguire}\\
\href{mailto:cv@finlaymagui.re}{cv@finlaymagui.re} | +44-77-6989-5717 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University College }
\runsubsection{London}\\
\descript{PhD in Bioinformatics}
\location{Dec 2015 | London, England}
Thesis: A multi-omic analysis of the photosynthetic endosymbioses of \textit{Paramecium bursaria} \\
\sectionsep

\subsection{Oxford University}
\descript{MA (hons) in Natural Science (Biological Sciences)}
\location{May 2011 | Oxford, England}
Dissertation: Evolution of the eukaryotic folate biosynthesis pathway\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Workshops}
\subsection{Taught}
Python and Advanced Python\\
Machine Learning for Life Sciences\\
Genomics and Transcriptomics\\
Unix and Perl\\
Image Processing with Python\\
Software Carpentry Bootcamp\\
Supervision of Masters and Undergraduate Researchers\\
\sectionsep

\subsection{Attended}
Gaussian Processes for Global Optimisation 2015\\
Gaussian Process Summer School 2015\\
EMBO YIP PhD Course 2013\\
Woods Hole Molecular Evolution Workshop 2012\\
MOOCs in Machine Learning, Mathematical Logic, Linear Algebra,
Databases, Algorithms, Analysis of Algorithms, 
Probabilistic Graphical Models, Statistics, Data Analysis,
Automata Theory, Music Theory\\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Python \textbullet{}  Shell \textbullet{} R \textbullet{} \LaTeX\ \\ 
\location{Over 1000 lines:}
C++ \textbullet{} matlab/octave \textbullet{} perl \textbullet{} CSS \textbullet{} AWK \textbullet{} SQL  \\
\location{Familiar:}
Verilog \textbullet{} Javascript (inc. D3.js) \textbullet{} Go
\textbullet{} HPC Linux Sysadmin \\
\sectionsep
\subsection{Molecular Biology}
\{transcript,gen,metabol\}-omics \textbullet{} 
nucleic acid extraction \textbullet{} culturing \textbullet{}
cloning \textbullet{} microscopy \\
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{University of Exeter}
\descript{| Postdoctoral Fellow}
\location{March 2016 - Present | Exeter, England}
\sectionsep
\begin{tightemize}
\item Analysing and simulating the evolution of protein transmembrane domains using deep recurrent neural networks
\item Automation of \textit{de novo} assembly hyperparameter selection via Bayesian optimisation
\item Evaluation of experimental induction and function of RNAi in a novel model organism.
\end{tightemize}

\runsubsection{Neuroglycerin}
\descript{| Technical Co-founder}
\location{Aug 2014 – Present | Edinburgh, Scotland}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Competitive Machine Learning Team.
\item Top 5\% finishes in two major international competitions.
\item Solutions coding collaboratively using standard software development methods (VCS, TDD).
\item Submissions include deep convolutional neural networks, model combining strategies, classical methods, computer vision, feature engineering approaches all used extensively in various competitions.
\end{tightemize}
\sectionsep

\runsubsection{NASA}
\descript{| Planetary Biology Fellow}
\location{July 2013 – Aug 2013 | Kennedy Space Center, Florida}
\begin{tightemize}
\item NASA representative and scientific adviser to BBC ``Cloud Lab'' Documentary.
\item Researched bacterial adaptations to extreme near-space conditions.
\item Designed and implemented trials for a stratospheric balloon flight.
\item Work resulted in a publication and journal front cover image.
\end{tightemize}
\sectionsep

\runsubsection{BioMAP Egypt}
\descript{| Research Assistant}
\location{July 2008 – Aug 2013 | Sinai, Egypt}
\begin{tightemize}
\item GIS project monitoring biodiversity in the Sinai Desert.
\item Involved in sampling, collection and preliminary data analysis in isolated and challenging conditions.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Conferences 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conferences}

\subsection{Invited Talks}
    Canadian Institute for Advanced Research IMB Meeting 2016 \textbullet{}
    Introduction to Machine Learning for Life Sciences Workshop 2015 \textbullet{}
EMBO YIP Meeting 2013\\
\subsection{Posters}

School of Informatics Jamboree 2015 \textbullet{} 
    EMBO: Comparative Genomics of Eukaryotic Microorganisms 2011 \& 2013 \textbullet{}
    National Association for Research in Science Teaching 2012 \textbullet{}
    Young Systematists Forum 2011 \textbullet{} SGM Summer Conference 2011 \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{-0.5cm}

\section{Awards} 
\begin{tabular}{rll}
2015	     & University  & Informatics Jamboree Prize \\
2015         & 57\textsuperscript{th}/1049 & National Data Science Bowl\\
2014         & 16\textsuperscript{th}/527 & American Epilepsy Society Seizure Prediction Challenge \\
2013	     & Global & NASA Planetary Biology Fellowship \\
2013	     & Global & Earth and Space Foundation Exploration Award\\
2010     & National & SGM Harry Smith Vacation Studentship\\
2009     & University & Dukinfield Exhibition in Biological Sciences\\
\end{tabular}
%Additionally, several meeting grants including FEMS Young Scientist Meeting Grants in 2013 and 2011, 
%and an SGM Meeting Grant in 2011.

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
%\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}
7 publications including Proceedings of the National Academy of Sciences, Royal Society B, and Current Biology.
See \url{goo.gl/04fiwt} for full citation list.

\end{minipage}
\end{document}  \documentclass[]{article}
